\section{Related Work}\label{sec:5related}

%Poor sleep can lead to numerous diseases, such as  endocrine dyscrasia, depression, immunity decline
%\cite{vgontzas2009insomnia,gottlieb2005association}. Thus, a lot of research works have been proposed to monitor the sleep
%\cite{langkvist2012sleep,hao2013isleep,bai2012will,kay2012lullaby,bain2003evaluation,pombo2016ubisleep}.

There is an extensive body work on sleep monitoring and
tracking~\cite{langkvist2012sleep,hao2013isleep,bai2012will,kay2012lullaby,bain2003evaluation,pombo2016ubisleep}. We summarize some of the
most relevant work in this section.

\subsection{Medical Grade Sleep Monitoring Solutions}
Traditionally, the dedicated medical technologies, like EEG, ECG and EMG \cite{saper2005hypothalamic}, have been applied for sleep
monitoring. Those technologies rely on the certain biomedical signals, such as brain wave, muscle tone and eye movement, to assess the
sleep quality. For example, the EEG technology in \cite{langkvist2012sleep,oropesa1999sleep,ebrahimi2008automatic} monitors the brain
waves, and then recognizes the sleep stages by leveraging unsupervised learning approaches. Although a high accuracy can be achieved by
those technologies, they have two drawbacks. First, those  technologies require the dedicated medical devices, which are expensive compared
the widely available smartwatch or smartphone. Second, they require the users to be attached many sensors on the human body, which may
cause a healthy person hard to sleep and result in large errors. Compared with those medical technologies, our system has two advantages.
First, we only need a smartwatch, which is more cost effective. Second, the smartwatch has little disruption to a user's normal sleep, thus
we can monitor the user's sleep quality more precisely.

\subsection{Smartphone-Based Approaches}
Numerous approaches have been proposed to exploit the use of a smartphone for sleep monitoring. iSleep \cite{hao2013isleep} measures the
sleep quality by recording sleep-related acoustic events and evaluates the sleep quality using the Pittsburgh Sleep Quality Index (PSQI)
\cite{carpenter1998psychometric}. Bai \etal~\cite{bai2012will} use a wide range of sensor data captured by the smartphone sensors,
including the accelerometer, gyroscope, and microphone, to predict a user's sleep quality. The work presented in \cite{kay2012lullaby}
leverages the smartphone sensors to record the sleep disruptor for a user, while the work presented in \cite{choe2011opportunities}
explores a series of opportunities to support healthy sleep behaviors. Other approaches predict the sleep quality by leveraging the
smartphone to monitor the external factors, such as the daily activity, the sleeping environment and location, and family settings
\cite{chen2013unobtrusive,zhang2013real}. In addition to the aforementioned approaches, there is a wide range of smartphone base sleep
monitoring applications. Examples of such applications include Sleep As Android \cite{SleepAndroid}, Sleep Journal \cite{SleepJournal}, and
YawnLog \cite{YawnLog}.

Those smartphone-based systems, however, require placing the smartphone at a specifically location near to the user, which may not always
be feasible. For example, the work presented in \cite{gu2016sleep} requires the smartphone to be placed next to the user's head, and to
remain stationary throughout the sleeping process. Such a constraint is hard to satisfy because of body movements during the sleep.
Furthermore, prior research also shows that many users do not want to place their mobile phone too close to the body due to health risk
concerns~\cite{StepHealth,Quorasleep}.

Unlike existing smartphone-based solutions, \systemname uses the commodity smartwatch for sleep monitoring. Since many users are willing to
wear a smartwatch throughout the sleep, the smartwatch can remain relatively close to the user body. This allows us to collect a wider
range of sleep-relevant events with a higher accuracy. This richer set of data thus leads to better sleep monitoring and quality
assessment.

\subsection{Wearable-Device-Based Approaches}
 With the widely use of wearable devices, more and more researchers and industries try to use the smartwatch or wearable-wrist for sleep
 monitoring \cite{bain2003evaluation,bonnet2003insomnia,pombo2016ubisleep,caviness1996myoclonus}. The Sleeptracker \cite{sleeptracker} is a
 wristwatch-shaped unit that apart from telling the time, also infers whether the user is in deep sleep, light sleep, or awake, using an
 accelerometer. The ubiSleep \cite{pombo2016ubisleep} joints heart rate, accelerometer, and sound signals collected into the smartwatch for
 noninvasive sleep monitoring. The aXbo alarm clock [9] is packaged as a stand-alone application in the form of an alarm clock that
 wirelessly communicates with a wrist-band unit. The Zeo \cite{caviness1996myoclonus} is similarly using an alarm clock base unit with a
 worn sensing device, but the latter is a headband rather than a wrist-band that based on electroencephalograph (EEG) to monitor sleep. We
 know Zeo has good performance in sleep stage detection compared to some wristband sleep monitoring products because products based on some
 biological signals like EEG are able to get more accurate and more representative sleep data than actigraphy-based \cite{Actigraphy} sleep
 monitoring products. However, the vast majority of biosignal-based sleep detection approaches require specialized equipment, which is high
 cost and complex to operate, while the approaches based on actigraphy are well
adapted and user-friendly to accept and understand.

Moreover, these actigraphy-based wristband devices or smartwatch Apps only can gather coarse-grained information and  do not design a model
for deep understanding the relationship between a user's sleep pattern and the sensor data. For example, many smartwatch Apps, like Jawbone
Up \cite{Jawbone}, FitBit \cite{fitbit}, YawnLog \cite{YawnLog} and WakeMate \cite{WakeMate}, do not show how they assess a user's sleep
quality based on what kind of sensor data. In addition,  there is some work that uses wearable devices to detect certain detailed events of
sleep. The work presented in \cite{wear_related2} detects roll-over and measure sleep quality using a wearable sensor. The approach
presented in \cite{wear_related3} uses a single chest-worn sensor to extract body acceleration and sleep position changes.


Compared with the existing smartwatch or wearable-wrist based systems, our system is a more complete sleep monitoring system, and is based
only on sensors in commercial smart watches without additional hardware. It collect an extensive set of sleep-related events, many of which
are not supported in prior work. And for sleep monitoring in daily life, it is more practical and will not invasion users' normal sleep ,
and more and more people are willing to accept to wear watches to fall asleep, unlike other wearable devices such as chest-worn sensors,
most people are still unwilling to accept to wear her to sleep. Moreover, our original intention and focus are more inclined to enable
users to have a deeper and more comprehensive understanding of their sleep, explore the causes of sleep quality, and provide users with
more practical advice to point them in a clear direction for improving sleep quality and being healthy.

In Table \ref{tab:function}, we compare {\systemname}'s functionalities with eight other existing sleep monitoring systems for mobile and
wearable devices. As can be seen from the table, {\systemname} supports the detection for the largest number of sleep related events, and
thus provides a rich set of sleep data.

%
\begin{table*}[!t]\footnotesize
 \setlength{\tabcolsep}{3pt}
\renewcommand{\arraystretch}{0.8}{\multirowsetup}{\centering}
  \caption{Compare the supporting functionalities of mobile based sleep monitoring systems.\label{tab:function}}
  \begin{tabular}{l cccccc}
        \toprule
       % \multirow{2}{*}{\textbf{System}} & \multicolumn{6}{c}{\textbf{Detected Events}} \\
%        \cline{2-7}
        & Heart Rate & Acoustic & Postures & Body Movements & Hand Positions & Sleep Stages \\
        \midrule
       \rowcolor{Gray} \systemname & &\checkmark&\checkmark&\checkmark&\checkmark&\checkmark\\
       Sleep as Andriod &  & \checkmark & & & & \checkmark \\
       \rowcolor{Gray} Sleep Hunter & & \checkmark &  & \checkmark & & \checkmark \\
       Sleep Monitor & &  & \checkmark &  & &  \\ %~\cite{sleepmonitor}
       \rowcolor{Gray} Sleeptracker & \checkmark &  &  & & & \checkmark \\ %~\cite{sleeptracker}
       isleep  && \checkmark & & \checkmark & & \\ %~\cite{hao2013isleep}
       \rowcolor{Gray} Fitbit & \checkmark &  & &  & & \checkmark \\
       Jawbone& &  & &  & & \checkmark \\ %~\cite{Jawbone}
       \rowcolor{Gray}  ubiSleep & \checkmark & \checkmark & &  & & \\ %~\cite{pombo2016ubisleep}
        \bottomrule
 \end{tabular}
\end{table*}



\subsection{Summary of Prior Work}
To summarize, as we can see from Table \ref{tab:related_work}, the advantage of {\systemname} is that it can detect more fine-grained sleep-related events to obtain more abundant sleep information, which is currently on the market for commercial or scientific research sleep monitoring system can not be achieved. And the performance of {\systemname} has been improved to some extent. Our original intention and focus are more inclined to enable users to have a deeper and more comprehensive understanding of their sleep, explore the cause s of sleep quality, and provide users with more practical advice to point them in a clear direction for improving sleep quality and being healthy. And compared with some medical technology like PSG, our advantages are inexpensive and easy to deploy at home, so it is suitable for most general public. And it does not need a large number of instruments attached to the user's body, thus it has less intrusiveness for sleep and does not require professional personnel to operate. Although the accuracy of {\systemname}'s ability to detect sleep cannot be compared to medical technology, it is enough for the average family's daily sleep monitoring needs. The most important is that we concentrates on physical activities rather than biomedical signals, so these rich physical activities detected are easily understood by users, and they can be adjusted with improved and improved sleep based on the results of monitoring.


\begin{table*}[!t]\footnotesize
 \setlength{\tabcolsep}{2.7pt}
\renewcommand{\arraystretch}{0.8}{\multirowsetup}{\centering}
  \caption{Summary of existing solutions.}\label{tab:related_work}
        \begin{tabular}{lcccccc}
        \toprule
        {System} & {High accuracy} & {Practicability} & {Low disruptive} & {Low cost} & {Informativeness} & {Interpretability}  \\
        \midrule
        \rowcolor{Gray} PSG     &  $\checkmark$ & &  &   & $\checkmark$ &  \\

        Smartphone& &$\checkmark$ &$\checkmark$  &$\checkmark$   & & $\checkmark$ \\

        \rowcolor{Gray} Wearable& &$\checkmark$ & $\checkmark$ & $\checkmark$  & & $\checkmark$ \\
        {\systemname} & &$\checkmark$ &$\checkmark$  & $\checkmark$  & $\checkmark$&$\checkmark$  \\

        \bottomrule
  \end{tabular}
\end{table*}
