\begin{abstract}
Sleep is an important part of our daily routine -- we spend about one-third of our time doing it. By tracking sleep-related events and
activities, sleep monitoring provides decision support to help us understand sleep quality and  causes of poor sleep. Wearable devices
provide a new way for sleep monitoring, allowing us to monitor sleep from the comfort of our own home. However, existing  solutions do
not take full advantage of the rich sensor data provided by these devices. In this paper, we present the design and development of
{\systemname}, a novel approach to track a wide range of sleep-related events using smartwatches. We show that using merely a single
smartwatch, it is possible to capture rich amount of information about sleep events and sleeping context, including body posture and
movements, acoustic events, and illumination conditions. We demonstrate that through these events it is possible to estimate sleep
quality and identify factors affecting it most. We evaluate our approach by conducting extensive experiments involved fifteen users
across a 2-week period. Our experimental results show that our approach can track a richer set of sleep events, provide better decision
support for evaluating sleep quality, and help to identify causes for sleep problems compared to prior work. %We also show that
%{\systemname} can help users to improve their sleep quality by having a better understanding of the root causes of sleep problems.
\end{abstract}


\begin{CCSXML}
	<ccs2012>
	<concept>
	<concept_id>10003120.10003138</concept_id>
	<concept_desc>Human-centered computing~Ubiquitous and mobile computing</concept_desc>
	<concept_significance>500</concept_significance>
	</concept>
	</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Human-centered computing~Ubiquitous and mobile computing} \keywords{Smartwatch sensing; mobile sensing; sleep events; sleep
monitoring}
